Depression and suicidality as credible signals of need

### 2021-05-07 Paper.rmd
Edited pilot study description and added discussion of possible anchor effects to the limitations.

We used the pilot data to estimate the sample sizes needed to detect an effect of the *Depression* signal vs. *Verbal request* control on *Belief* in the victim's need. Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`. We also estimated the sample size needed to detect an effect of *Depression* vs. a *Control* condition that was meant to not include any signaling (but which we realized, post hoc, did include a verbal request). Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`. See Figure \@ref(fig:power). Given our \$1500 USD budget, we aimed for a sample size of 124 for treatment plus control conditions, and 1240 for all conditions in the study. For more details, see the SI.

@@

In terms of data quality our largest limitation is that, compared to the US sample, far more Indian participants were filtered out by our attention checks, something which could be consistent with botting, unfamiliarity with English, or low effort responses [@kennedy2020]. Assuming this corresponded with lower-quality responses among those who passed the attention checks, the weak signal effect in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenario or the effectiveness of the signals compared to those in the US.

>>>>

We used the pilot data to estimate the sample sizes needed to detect an effect of the *Depression* signal vs. *Verbal request* control on *Belief* in the victim's need. Power was about 80% for a sample size of about `r pwr80_90[[2,2]]`, and was about 90% for a sample size of about `r pwr80_90[[2,3]]`. We also estimated the sample size needed to detect an effect of *Depression* vs. a *Control* condition in which there was only a verbal request made in the body of the vignette, with no signal given during a second encounter (when signaling was manipulated). Power was about 80% for a sample size of about `r pwr80_90[[1,2]]`, and was about 90% for a sample size of about `r pwr80_90[[1,3]]`. See Figure \@ref(fig:power). Given our \$1500 USD budget, we aimed for a sample size of 124 for treatment plus control conditions, and 1240 for all conditions in the study. For more details, see the SI.

@@

In terms of data quality our largest limitation is that, compared to the US sample, far more Indian participants were filtered out by our attention checks, something which could be consistent with botting, unfamiliarity with English, or low effort responses [@kennedy2020]. Assuming this corresponded with lower-quality responses among those who passed the attention checks, the weak signal effect in the thwarted marriage vignette may simply be due to added noise rather than differences in the scenario or the effectiveness of the signals compared to those in the US. Another concern relevant to all vignettes is that our decision to anchor the T1 sliders at 0 may have resulted in participants being more likely to report extreme values.
